%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muhammad Ahmad Usama} \\ \vspace{1pt}
    \small +923028565399 $|$ \href{mailto:ahmedusama723@gmail.com}{\underline{ahmedusama723@gmail.com}} $|$
    \href{https://linkedin.com/in/mrahmadusama}{\underline{linkedin.com/in/mrahmadusama}} $|$
    \href{https://mrahmadusama.com/}{\underline{mrahmadusama.com}}
\end{center}


%-----------SUMMARY-----------
\section{Professional Summary}
  \small{UX and CX Designer with 4+ years of experience turning complex systems into intuitive, user-friendly products. Works at the intersection of design, business, and technology, applying Design Thinking and Service Design to create meaningful digital experiences. Actively incorporates AI tools like ChatGPT and Claude into every stage of the workflow---from research and ideation to design systems---to move faster and make smarter decisions. Experienced in collaborating with stakeholders across fintech and government sectors, aligning user needs with business goals and contributing to large-scale digital transformation projects.}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior UX Designer}{Jan 2025 -- Present}
      {Adalfi -- a Techlogix company}{Lahore, PK}
      \resumeItemListStart
        \resumeItem{Designed complete mobile experiences for an AI-powered digital lending platform, supporting products like salary advances, personal loans, and credit cards across multiple banks.}
        \resumeItem{Integrated AI tools into daily workflows, using them for research, UX writing, prototyping, and managing design systems more efficiently.}
        \resumeItem{Built and maintained a scalable Figma design system, improving consistency across products and making collaboration with developers smoother.}
        \resumeItem{Focused on creating fast, engaging user flows---helping reduce loan processing time to under 60 seconds through thoughtful UI and interaction design.}
      \resumeItemListEnd

    \resumeSubheading
      {UX Designer}{Aug 2022 -- Dec 2024}
      {Techlogix}{Lahore, PK}
      \resumeItemListStart
        \resumeItem{Led a process redesign project for SECP that improved service efficiency by 25\% for thousands of monthly users.}
        \resumeItem{Simplified complex internal workflows across multiple departments, cutting processing time by 40\%.}
        \resumeItem{Ran design thinking workshops to bring teams together, generate ideas, and validate solutions.}
        \resumeItem{Created service blueprints and optimized user journeys to improve both operational performance and user satisfaction.}
        \resumeItem{Worked closely with business and technical teams to translate complex systems into clear, user-friendly experiences.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Engineering and Technology}{Lahore, PK}
      {Master of Science in Computer Science, Major in Information Systems}{2024}
    \resumeSubheading
      {University of Engineering and Technology}{Lahore, PK}
      {Bachelor of Science in Computer Science, Major in Human Computer Interaction}{2022}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SECP -- eZfile} $|$ \emph{UX Research, Service Design, Design Thinking, Figma}}{2023 -- 2025}
          \resumeItemListStart
            \resumeItem{Comprehensive digital solution for the Securities and Exchange Commission of Pakistan to streamline and digitize the regulatory filing process.}
            \resumeItem{Designed an intuitive, user-friendly interface simplifying submission of legal and financial documents, enhancing efficiency and accuracy of filings for businesses across Pakistan.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal Portfolio Website} $|$ \emph{Vibe Coding, Next.js, React, Tailwind CSS, Claude Code}}{2025}
          \resumeItemListStart
            \resumeItem{Designed and vibe-coded a personal portfolio from scratch using AI-assisted development with Claude Code and Cursor, translating UX design skills into a fully functional, responsive website.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Agri Business Mobile Application} $|$ \emph{UX Case Study, Mobile Design}}{2022}
          \resumeItemListStart
            \resumeItem{Designed a case study mobile application for different categories of agribusiness.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{A1A Carwash App Design} $|$ \emph{UI/UX Case Study, Sitemaps, Wireframing}}{2021}
          \resumeItemListStart
            \resumeItem{Created mobile application design including UI/UX case study, sitemaps, and wireframing.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{UX Skills}{: UX Research, UI Prototyping, Wireframing, Interaction Design, Design Systems, Information Architecture} \\
     \textbf{Design Tools}{: Figma Design, Figma Make (AI), Adobe Creative Suite, JustInMind, Canva, HTML/CSS} \\
     \textbf{AI-Augmented Design}{: ChatGPT (UX Research \& Copywriting), Claude Code (Figma Ideation \& Design System Mgmt), Cursor, V0, AI Prompt Engineering} \\
     \textbf{Methodologies}{: Design Thinking, User-Centered Design, Agile UX, Accessibility Standards, UX Strategy \& Consulting} \\
     \textbf{Development}{: Vibe Coding, React, Next.js, Tailwind CSS, HTML/CSS, Git}
    }}
 \end{itemize}


%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{User Experience (UX): The Ultimate Guide to Usability and UX} $|$ \emph{Udemy}}{Nov 2023}
      \resumeProjectHeading
          {\textbf{Start the UX Design Process: Empathize, Define, and Ideate} $|$ \emph{Google Career Certificates}}{May 2023}
      \resumeProjectHeading
          {\textbf{Foundations of User Experience (UX) Design} $|$ \emph{Google Career Certificates}}{Jan 2023}
    \resumeSubHeadingListEnd


%-----------WORKSHOPS-----------
\section{Workshops}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Design Thinking Workshop Phase 1B} -- SECP 'Ezfile' Digital Transformation}{Feb 2023}
          \resumeItemListStart
            \resumeItem{Conducted in collaboration with SECP, Ernst \& Young (EY) and Techlogix.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Design Thinking Workshop Phase 2A} -- SECP 'Ezfile' Digital Transformation}{May 2024}
          \resumeItemListStart
            \resumeItem{Conducted in collaboration with SECP, Ernst \& Young (EY) and Techlogix.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Advanced (C1)} \quad
     \textbf{Urdu}{: Native}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
